---
title: Impact of AusTraits
widget: blank
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)

library(blogdown)
library(scholar)
library(dplyr)
```


<script type="text/javascript" src="https://d1bxh8uas1mnw7.cloudfront.net/assets/embed.js"></script>/div>

By providing a curated, open source and FAIR big data resource, AusTraits aims to transform research on the Australian flora. This page tracks our impact to date. The page was last updated on `r Sys.Date()`. For the latest impact, see links provided below.

## Dataset downlaods

AusTraits is provided as an open access data set via Zenodo, with multiple releases available, grouped under a "Concept DOI": [![DOI](https://zenodo.org/badge/DOI/10.5281/zenodo.3583418.svg)](https://doi.org/10.5281/zenodo.3583418) 

[Zenodo tracks](https://www.projectcounter.org/code-practice-research-data/repositories-that-have-implemented-the-code-of-practice-for-research-data/) usage of AusTraits, following the [Counter Code of Practive for Research Data](https://www.projectcounter.org/code-practice-research-data/). The latest values are available at the above link. As of  `r Sys.Date()` the data has been accessed as follows:

```{r}
link <- "https://zenodo.org/api/records/3568417"

# Issue -- Visiting the link via browser returns a json including stats, but 
# these are missing when querying via R???
# x <- httr::GET(link, httr::add_headers(`Content-Type`=  "application/json")) %>% 
#  httr::content(as = "text") %>% jsonlite::fromJSON()
# names(x)

json_3568417 <- readLines(link) 
writeLines(json_3568417, paste("3568417.json"))

x <- json_3568417 %>% jsonlite::fromJSON()

# Extract stats
stats_3568417 <- tibble(
  Metric = 
  c(
    "Views", "Downloads", "Unique views", "Unique downloads", "Data volume (MB)"
  ), 
  `Latest version` = 
  c(
    x$stats$views, 
    x$stats$downloads, 
    x$stats$unique_views,
    x$stats$unique_downloads, 
    format(x$stats$volume/1E6, digits = 0)
  ),
  `All versions` = 
  c(
    x$stats$version_views, 
    x$stats$version_downloads, 
    x$stats$version_unique_views,
    x$stats$version_unique_downloads, 
    format(x$stats$version_volume/1E6, digits = 0)
  ))

stats_3568417 %>% kableExtra::kable()
```

    
## Data Descriptor
```{r}
cites_austraits <- scholar::get_article_cite_history("QXMISwEAAAAJ", "K3LRdlH-MEoC")
```

The original paper describing AusTraits data was published in *Scientific Data*:

* Falster, Gallagher, Wenk, Wright, Indiarto, Andrew, ... (2021) AusTraits, a curated plant trait database for the Australian flora. *Scientific data*: 8 (1), 1-20 [10.1038/s41597-021-01006-6](http://doi.org/10.1038/s41597-021-01006-6). 

Thus far, the paper has been cited [`r sum(cites_austraits$cites)` times](https://scholar.google.com/citations?view_op=view_citation&hl=en&user=QXMISwEAAAAJ&sortby=pubdate&citation_for_view=QXMISwEAAAAJ:K3LRdlH-MEoC
), as indicated by Google Scholar. 

The Altmetics of the paper capture it's broader coverage for further details see the [articles metrics page](https://nature.altmetric.com/details/114271024): 

<div data-badge-details="right" data-badge-type="donut" data-doi="10.1038/s41597-021-01006-6" data-condensed="true" class="altmetric-embed"></div>


Below is a selection of papers using the AusTraits database:

```{r, results='asis'}
data <- 
  scholar::get_publications("VFFY9AQAAAAJ") %>% as_tibble() %>%
  filter(pubid != "u-x6o8ySG0sC") %>%
  arrange(desc(year)) %>%
  mutate(
       link = sprintf("https://scholar.google.com/citations?view_op=view_citation&citation_for_view=VFFY9AQAAAAJ:%s", pubid),
       cite =  sprintf("- %s (%s) %s. *%s*: %s [link](%s)", author, year, title, journal, number, link)
  )

data$cite %>% writeLines()
```

## Social media

Here are of the nice things the community is saying about AusTraits --

`r blogdown::shortcode("tweet", id= "1463020322274234370", user = "hj_whiterabbit")`

`r blogdown::shortcode("tweet", id= "1463421260076138499", user = "nicrodemo")`

`r blogdown::shortcode("tweet", id= "1448168356218118144", user = "SallyArchibald")`

`r blogdown::shortcode("tweet", id= "1444438004802592768", user = "davidtng")`

`r blogdown::shortcode("tweet", id= "1448452700123795458", user = "hsauquet_rbgsyd")`

`r blogdown::shortcode("tweet", id= "1448393376735264768", user = "rubyecology")`

`r blogdown::shortcode("tweet", id= "1445575788867248129", user = "ARDC_AU")`

